---
title: "2yp_prelim_graph"
author: "Rui"
date: "3/29/2021"
output: html_document
---

# Data Preparation

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(caret)
library(stargazer)
library(broom)
library(did)
library(pscl)
library(mfx)
library(psych)
library(rstatix)
library(ggpubr)
```

```{r}
df = read.csv('D:/2yp/cleaned_data/concat_210502.csv')
df = df %>% 
  mutate(twocp = ifelse(year>2015, 1, 0),
         major_city = 1-minor_city,
         first.treat = ifelse(major_city, 2016, 0),
         twocp_cont = year-2016,
         no_elig_ratio = pre_job_no/elig_pop,
         base_level = ifelse(level==3, 1, 0))
         #level0 = ifelse(level==0, 1, 0),
         #level1 = ifelse(level==1, 1, 0),
         #level2 = ifelse(level==2, 1, 0),
         #level3 = ifelse(level==3, 1, 0),
         #ethnic_all = ifelse(ethnic=='all', 1, 0),
         #ethnic_minor = ifelse(ethnic=='minority', 1, 0),
         #ethnic_han = ifelse(ethnic=='han', 1, 0)
```
```{r}

hist(agg_depar$depar_gsr_m_ratio)
```


```{r}
df_wo_police = df %>% filter(police==0)
df_w_police = df %>% filter(police==1)

df_wo_tibet = df %>% filter(region0_eng!='tibet')
df_wo_xinjiang = df %>%  filter(region0_eng!='xinjiang')
df_wo_police_tibet = df_wo_police %>%  filter(region0_eng!='tibet')
df_wo_police_xinjiang = df_wo_police %>% filter(region0_eng!='xinjiang')

#write.csv(df_wo_police_tibet,"C:/Users/lenovo/Desktop/prelim_graph/data/wo_police_tibet_210417_stata.csv", row.names = FALSE)
```
```{r}
agg_depar = read.csv('D:/2yp/cleaned_data/agg_depar_210503.csv')
agg_depar = agg_depar %>% 
  mutate(twocp = ifelse(year>2015, 1, 0),
         major_city = 1-minor_city,
         first.treat = ifelse(major_city, 2016, 0),
         twocp_cont = year-2016,
         no_elig_ratio = pre_job_no/elig_pop,
         base_level = ifelse(level>2, 1, 0))

agg_pre = read.csv('D:/2yp/cleaned_data/agg_pre_210503.csv')
agg_pre = agg_pre %>% 
  mutate(twocp = ifelse(year>2015, 1, 0),
         major_city = 1-minor_city,
         first.treat = ifelse(major_city, 2016, 0),
         twocp_cont = year-2016,
         no_elig_ratio = pre_job_no/elig_pop) 
```


```{r}
df_wo_police = df_wo_police %>% 
  mutate(yr2014=ifelse(year==2014,1,0),
         yr2015=ifelse(year==2015,1,0),
         yr2016=ifelse(year==2016,1,0),
         yr2017=ifelse(year==2017,1,0),
         yr2018=ifelse(year==2018,1,0),
         yr2019=ifelse(year==2019,1,0))
df_wo_police_tibet = df_wo_police_tibet %>% 
  mutate(yr2014=ifelse(year==2014,1,0),
         yr2015=ifelse(year==2015,1,0),
         yr2016=ifelse(year==2016,1,0),
         yr2017=ifelse(year==2017,1,0),
         yr2018=ifelse(year==2018,1,0),
         yr2019=ifelse(year==2019,1,0))
```

```{r,echo=FALSE}
  # df_wo_police %>%
  # group_by(region1,year)
  # summarize(count = n(),
  #           sum_gsr_m_no = sum(gsr_m_no),
  #           sum_gsr_f_no = sum(gsr_f_no),
  #           sum_job_no = sum(job_no),
  #           sum_gsr_m = sum(gsr_m),
  #           sum_gsr_f = sum(gsr_f)) %>%
  # mutate(major_city = 1-minor_city,
  #        twocp = ifelse(year>2015, 1, 0),
  #        gsr_m_por_ppl = sum_gsr_m_no*100/sum_job_no,
  #        gsr_f_por_ppl = sum_gsr_f_no*100/sum_job_no,
  #        gsr_m_por_job = sum_gsr_m*100/count,
  #        gsr_f_por_job = sum_gsr_f*100/count)
```

# summary statistics

```{r}
df_wo_police_major = df_wo_police%>%filter(major_city==1)
df_wo_police_minor = df_wo_police%>%filter(minor_city==1)
#df_wo_police_minor2013 =  df_wo_police%>%filter(year == 2013 & major_city==0)
stargazer(df_wo_police_minor, df_wo_police_major , summary=TRUE,style='aer')
#t.test(job_no ~ major_city, data = df_wo_police)
```

```{r}
mydata = df %>% dplyr::select(pop_minority_ratio, pop_total, avg_educ_total, major_city)

mydata.long <- mydata %>%
  pivot_longer(-major_city, names_to = "variables", values_to = "value")

stat.test <- mydata.long %>%
  group_by(variables) %>%
  t_test(value ~ major_city) %>%
stat.test

```


```{r}
t_test = t.test(job_no ~ major_city, data = df_wo_police)
t_test$estimate
```

# Prelim Graphs

## Non-police jobs, by minority city

```{r,echo=FALSE}
police0minor = ggplot(NULL, aes(x=year)) + 
  geom_line(data = df_sum[df_sum$police ==0 & df_sum$minor_city ==0,], aes(y = gsr_f_por_job,color='% of GSR female, majority'),size=1) +
  geom_line(data = df_sum[df_sum$police ==0 & df_sum$minor_city ==0,], aes(y = gsr_m_por_job,color='% of GSR male, majority'),size=1) +
  geom_line(data = df_sum[df_sum$police ==0 & df_sum$minor_city ==1,], aes(y = gsr_f_por_job,color='% of GSR female, minority'),size=1) +
  geom_line(data = df_sum[df_sum$police ==0 & df_sum$minor_city ==1,], aes(y = gsr_m_por_job,color='% of GSR male, minority'),size=1) +
  geom_vline(aes(xintercept=2017, color = 'UTCP enacted'),size=1)+
  labs(title = "% of Gender Specific Requirement (GSR) non-police, 2013-2020", x = "Year", y = "% of GSR Jobs", color = 'Colors') 
#  scale_color_manual(labels = c('% of gsr female, non-minority', '% of gsr male, non-minority'), values = c('navy', "darkred")) 

police0minor
```


## Police jobs, by minority city


```{r,echo=FALSE}
police1minor = ggplot(NULL, aes(x=year)) + 
  geom_line(data = df_sum[df_sum$police ==1 &df_sum$minor_city ==0,], aes(y = gsr_f_por_job,color='% of GSR female, non-minority'),size = 1) +
  geom_line(data = df_sum[df_sum$police ==1 &df_sum$minor_city ==0,], aes(y = gsr_m_por_job,color='% of GSR male, non-minority'),size = 1) +
  geom_line(data = df_sum[df_sum$police ==1 &df_sum$minor_city ==1,], aes(y = gsr_f_por_job,color='% of GSR female, minority'),size = 1) +
  geom_line(data = df_sum[df_sum$police ==1 &df_sum$minor_city ==1,], aes(y = gsr_m_por_job,color='% of GSR male, minority'),size = 1) +
  geom_vline(aes(xintercept=2017, color = 'Two Child Policy'),size=1)+
  labs(title = "% of Gender Specific Requirement (GSR) police, 2013-2020", x = "Year", y = "% of GSR Jobs", color = "Color")
#  scale_color_manual(labels = c('% of gsr female, non-minority', '% of gsr male, non-minority'), values = c('navy', "darkred"))
  
police1minor
```


```{r,echo=FALSE}
minor = ggplot(NULL, aes(x=year)) + 
  geom_line(data = df_sum1[df_sum1$minor_city ==0,], aes(y = gsr_f_por_job,color='% of GSR female, non-minority'),size = 1) +
  geom_line(data = df_sum1[df_sum1$minor_city ==0,], aes(y = gsr_m_por_job,color='% of GSR male, non-minority'),size = 1) +
  geom_line(data = df_sum1[df_sum1$minor_city ==1,], aes(y = gsr_f_por_job,color='% of GSR female, minority'),size = 1) +
  geom_line(data = df_sum1[df_sum1$minor_city ==1,], aes(y = gsr_m_por_job,color='% of GSR male, minority'),size = 1) +
  geom_vline(aes(xintercept=2017, color = 'Two Child Policy'),size=1)+
  labs(title = "% of Gender Specific Requirement (GSR) pooled, 2013-2020", x = "Year", y = "% of GSR Jobs", color = "Color")
#  scale_color_manual(labels = c('% of gsr female, non-minority', '% of gsr male, non-minority'), values = c('navy', "darkred")) 

minor
```


## Event Study

```{r}
## define function that draws event study plot
event_plot = function(outvar_str,dataset) {
  did.att.gt = att_gt(yname=outvar_str,
                     tname="year",
                    idname='X',
                     gname="first.treat",
                    panel = FALSE,
                     data=dataset)
  #summary(did.att.gt)
  # aggregate them into event study plot
  did.es <- aggte(did.att.gt, type="dynamic")

  # plot the event study
  ggdid(did.es)
}
```

```{r}
event_plot("gsr_m",df_wo_police)
```



# regressions

## DID 

### without interactions

```{r}
#define regression function
lm_did = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$gsr_f
    dep_var_1 = dataset_1$gsr_f_no
  }else{
    dep_var_0 = dataset_0$gsr_m
    dep_var_1 = dataset_1$gsr_m_no
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city + depar_job_no , data=dataset_0)
  #gsr_lm1 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil, data=dataset)
  #gsr_lm2 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) , data=dataset)
  #gsr_lm3 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level), data=dataset)
  gsr_lm4 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year)+ depar_job_no, data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng)+ depar_job_no, data=dataset_0)  
  
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + depar_job_no, data=dataset_1)
  gsr_no_lm4 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year)+ depar_job_no, data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng)+ depar_job_no, data=dataset_1)  
  
  #cluster standard error by province
  gsr_lm0_se = coef(summary(gsr_lm0,cluster='region1'))[,2]
  gsr_lm4_se = coef(summary(gsr_lm4,cluster='region1'))[,2]
  gsr_lm5_se = coef(summary(gsr_lm5,cluster='region1'))[,2]
  gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='region1'))[,2]
  gsr_no_lm4_se = coef(summary(gsr_no_lm4,cluster='region1'))[,2]
  gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='region1'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm4, gsr_lm5, gsr_no_lm0, gsr_no_lm4, gsr_no_lm5,
            se=list(gsr_lm0_se,gsr_lm4_se,gsr_lm5_se,gsr_no_lm0_se,gsr_no_lm4_se,gsr_no_lm5_se),
            omit = c('Constant','region0_eng','year'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```

### zero inflated and logit regression

```{r}
#define regression function
probit_zeroinfl_did = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$gsr_f
    dep_var_1 = dataset_1$gsr_f_no
  }else{
    dep_var_0 = dataset_0$gsr_m
    dep_var_1 = dataset_1$gsr_m_no
  }
  
  #by jobs
  gsr_lm0 = glm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city ,
                family = binomial(link = "probit"), data=dataset_0)
  #gsr_lm1 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil, data=dataset)
  #gsr_lm2 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) , data=dataset)
  #gsr_lm3 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level), data=dataset)
  gsr_lm4 = glm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year), 
                family = binomial(link = "probit"), data=dataset_0)
  gsr_lm5 = glm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng), 
                family = binomial(link = "probit"), data=dataset_0)  
  
  
  #by headcounts
  gsr_no_lm0 = zeroinfl(formula = dep_var_1 ~  twocp:major_city + twocp + major_city,
                        data=dataset_1)
  gsr_no_lm4 = zeroinfl(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + + yr2014 + yr2015 + yr2016 + yr2017 + yr2018 + yr2019,
                        data=dataset_1)
  gsr_no_lm5 = zeroinfl(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + yr2014 + yr2015 + yr2016 + yr2017 + yr2018 + yr2019 + factor(region0_eng)
                        , data=dataset_1)  
  
  #cluster standard error by province
  gsr_lm0_se = coef(summary(gsr_lm0,cluster='region1'))[,2]
  gsr_lm4_se = coef(summary(gsr_lm4,cluster='region1'))[,2]
  gsr_lm5_se = coef(summary(gsr_lm5,cluster='region1'))[,2]
  gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='region1'))[2][[1]][,2]
  gsr_no_lm4_se = coef(summary(gsr_no_lm4,cluster='region1'))[2][[1]][,2]
  gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='region1'))[2][[1]][,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm4, gsr_lm5, gsr_no_lm0, gsr_no_lm4, gsr_no_lm5,
            se=list(gsr_lm0_se,gsr_lm4_se,gsr_lm5_se,gsr_no_lm0_se,gsr_no_lm4_se,gsr_no_lm5_se),
            omit = c('Constant','region0_eng','year','yr2014','yr2015','yr2016','yr2017','yr2018','yr2019'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c("f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```


```{r}
#lm_gsr_f = lm_did('female', df_wo_police, df_wo_police_tibet)
lm_gsr_m = lm_did('male', df_wo_police, df_wo_police_tibet)
#probit_zeroinfl_gsr_f = probit_zeroinfl_did('female', df_wo_police, df_wo_police_tibet)
#probit_zeroinfl_gsr_m = probit_zeroinfl_did('female', df_wo_police, df_wo_police_tibet)
#lm_gsr_m = lm_did('male', df_wo_police, df_wo_police_tibet)
```

```{r}
#zeroinfl_test = zeroinfl(formula = gsr_m_no ~ twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year), data=df_wo_police_tibet)
#coef(summary(glm_test,cluster='region1'))#[,2]
#hist(df_wo_police_tibet$gsr_f_no)
#probitmfx(formula = gsr_m ~ twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + yr2014 + yr2015 + yr2016 + yr2017 + yr2018 + yr2019 + factor(region0_eng), data=df_wo_police)
#zeroinfl_test = zeroinfl(formula = gsr_m_no ~ twocp:major_city + twocp + major_city + yr2014 + yr2015 + yr2016 + yr2017 + yr2018 + yr2019, data = df_wo_police_tibet)

```

### with interactions, heterogeneity

```{r}
 #define regression function
 lm_did_wo_police_inter = function(dataset){
   #female
   #gsr_f_lm0 = lm(formula = gsr_f_no ~  twocp:major_city + twocp + major_city , data=dataset)
   #gsr_lm1 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil, data=dataset)
   #gsr_lm2 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) , data=dataset)
   #gsr_lm3 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level), data=dataset)
   gsr_f_lm4 = lm(formula = gsr_f ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + twocp:factor(ethnic) + factor(level) + twocp:factor(level) + factor(year), data=dataset)
   gsr_f_lm5 = lm(formula = gsr_f ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + twocp:factor(ethnic) + factor(level) + twocp:factor(level) + factor(year) + factor(region0_eng), data=dataset)


   #male
   #gsr_m_lm0 = lm(formula = gsr_m_no ~  twocp:major_city + twocp + major_city , data=dataset)
   gsr_m_lm4 = lm(formula = gsr_m ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + twocp:factor(ethnic) + factor(level) + twocp:factor(level) + factor(year), data=dataset)
   gsr_m_lm5 = lm(formula = gsr_m ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + twocp:factor(ethnic) + factor(level) + twocp:factor(level) + factor(year) + factor(region0_eng), data=dataset)

   #cluster standard error by province
   #gsr_f_lm0_se = coef(summary(gsr_f_lm0,cluster='region1'))[,2]
   gsr_f_lm4_se = coef(summary(gsr_f_lm4,cluster='region1'))[,2]
   gsr_f_lm5_se = coef(summary(gsr_f_lm5,cluster='region1'))[,2]
   #gsr_m_lm0_se = coef(summary(gsr_m_lm0,cluster='region1'))[,2]
   gsr_m_lm4_se = coef(summary(gsr_m_lm4,cluster='region1'))[,2]
   gsr_m_lm5_se = coef(summary(gsr_m_lm5,cluster='region1'))[,2]

   #regression table setup
   stargazer(gsr_f_lm4, gsr_f_lm5, gsr_m_lm4, gsr_m_lm5,
             se=list(gsr_f_lm4_se,gsr_f_lm5_se,gsr_m_lm4_se,gsr_m_lm5_se),
             omit = c('Constant','region0_eng','year'),
             covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture','UTCP*ethnicity: Han','UTCP*ethnicity: minority','UTCP*level: prefecture[1]', 'UTCP*level: county[2]', 'UTCP*level: township[3]'),
             omit.stat = c('rsq',"f",'ser'),
             add.lines = list(c("Year Fixed effect", "Y", 'Y','Y','Y'),
                            c("Province Fixed effect",  "N", 'Y','N','Y')),
             style='aer',
             title="UTCP and Gender Specific Requirement",
             column.labels   = c("headcounts specify female", "headcounts specify male"),
             column.separate = c(2, 2),
             align=TRUE)
 }
```

### add pre level control variables

#### dependent variable at job level

```{r}
#define regression function
lm_did_control = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$gsr_f
    dep_var_1 = dataset_1$gsr_f_no
  }else{
    dep_var_0 = dataset_0$gsr_m
    dep_var_1 = dataset_1$gsr_m_no
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city , data=dataset_0)
  #gsr_lm1 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil, data=dataset)
  #gsr_lm2 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) , data=dataset)
  #gsr_lm3 = lm(out_var ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level), data=dataset)
  #gsr_lm4 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year)+ depar_job_no, data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng), data=dataset_0)  
  gsr_lm6 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city +  non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_0)
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city, data=dataset_1)
  #gsr_no_lm4 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year)+ depar_job_no, data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city  + non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng), data=dataset_1)
  gsr_no_lm6 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city +  non_civil + factor(ethnic) + factor(level) + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_1)
  
  #cluster standard error by province
  gsr_lm0_se = coef(summary(gsr_lm0,cluster='depar_total'))[,2]
  gsr_lm5_se = coef(summary(gsr_lm5,cluster='depar_total'))[,2]
  gsr_lm6_se = coef(summary(gsr_lm6,cluster='depar_total'))[,2]
  gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='depar_total'))[,2]
  gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='depar_total'))[,2]
  gsr_no_lm6_se = coef(summary(gsr_no_lm6,cluster='depar_total'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm5, gsr_lm6, gsr_no_lm0, gsr_no_lm5, gsr_no_lm6,
            se=list(gsr_lm0_se,gsr_lm5_se,gsr_lm6_se,gsr_no_lm0_se,gsr_no_lm5_se,gsr_no_lm6_se),
            omit = c('Constant','region0_eng','year'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "Y", 'Y','N','Y','Y'),
                           c("Aggregate Control",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```

#### dependent variable at department level 

```{r}
#define regression function
lm_did_control_depar = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$depar_gsr_f_ratio
    dep_var_1 = dataset_1$depar_gsr_f_no_ratio
  }else{
    dep_var_0 = dataset_0$depar_gsr_m_ratio
    dep_var_1 = dataset_1$depar_gsr_m_no_ratio
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city , data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + factor(level) + factor(year) + factor(region0_eng), data=dataset_0)  
  gsr_lm6 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city + factor(level) + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_0)
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city, data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + factor(level) + factor(year) + factor(region0_eng), data=dataset_1)
  gsr_no_lm6 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + factor(level) + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_1)
  
  #cluster standard error by province
  # gsr_lm0_se = coef(summary(gsr_lm0,cluster='depar_total'))[,2]
  # gsr_lm5_se = coef(summary(gsr_lm5,cluster='depar_total'))[,2]
  # gsr_lm6_se = coef(summary(gsr_lm6,cluster='depar_total'))[,2]
  # gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='depar_total'))[,2]
  # gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='depar_total'))[,2]
  # gsr_no_lm6_se = coef(summary(gsr_no_lm6,cluster='depar_total'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm5, gsr_lm6, gsr_no_lm0, gsr_no_lm5, gsr_no_lm6,
            #se=list(gsr_lm0_se,gsr_lm5_se,gsr_lm6_se,gsr_no_lm0_se,gsr_no_lm5_se,gsr_no_lm6_se),
            omit = c('Constant','region0_eng','year','level'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "Y", 'Y','N','Y','Y'),
                           c("Aggregate Control",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```

#### dependent variable at prefecture level 

```{r}
#define regression function
lm_did_control_pre = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$pre_gsr_f_ratio
    dep_var_1 = dataset_1$pre_gsr_f_no_ratio
  }else{
    dep_var_0 = dataset_0$pre_gsr_m_ratio
    dep_var_1 = dataset_1$pre_gsr_m_no_ratio
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city , data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + factor(year) + factor(region0_eng), data=dataset_0)  
  gsr_lm6 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city  + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_0)
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city, data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + factor(year) + factor(region0_eng), data=dataset_1)
  gsr_no_lm6 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + factor(year) + factor(region0_eng) + pop_total + pop_minority_ratio + avg_educ_total + no_elig_ratio, data=dataset_1)
  
  #cluster standard error by province
  # gsr_lm0_se = coef(summary(gsr_lm0,cluster='region1'))[,2]
  # gsr_lm5_se = coef(summary(gsr_lm5,cluster='region1'))[,2]
  # gsr_lm6_se = coef(summary(gsr_lm6,cluster='region1'))[,2]
  # gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='region1'))[,2]
  # gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='region1'))[,2]
  # gsr_no_lm6_se = coef(summary(gsr_no_lm6,cluster='region1'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm5, gsr_lm6, gsr_no_lm0, gsr_no_lm5, gsr_no_lm6,
            #se=list(gsr_lm0_se,gsr_lm5_se,gsr_lm6_se,gsr_no_lm0_se,gsr_no_lm5_se,gsr_no_lm6_se),
            omit = c('Constant','region0_eng','year'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "Y", 'Y','N','Y','Y'),
                           c("Aggregate Control",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```

```{r}
#lm_gsr_f_control = lm_did_control('female', df_wo_police, df_wo_police_tibet)
#lm_gsr_m_control = lm_did_control('male', df_wo_police, df_wo_police_tibet)
#lm_gsr_f_control_depar = lm_did_control_depar('female', agg_depar, agg_depar)
#lm_gsr_m_control_depar = lm_did_control_depar('male', agg_depar, agg_depar)
lm_gsr_f_control_pre = lm_did_control_pre('female', agg_pre, agg_pre)
#lm_gsr_m_control_pre = lm_did_control_pre('male', agg_depar, agg_depar)
```
```{r}
hist(agg_pre$pre_gsr_m_ratio)
```

## event study DID

### without police

```{r}
#define regression function
lm_event_did = function(gender, dataset_0, dataset_1){
  
  if(gender == 'female'){
    out_var_0 = dataset_0$gsr_f
    out_var_1 = dataset_1$gsr_f_no
  }else{
    out_var_0 = dataset_0$gsr_m
    out_var_1 = dataset_1$gsr_m_no
  }
  
  gsr_cont_lm0 = lm(out_var_0 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city, data=dataset_0)
  #gsr_cont_lm1 removed because has police
  #gsr_cont_lm2 = lm(out_var ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city +  non_civil + factor(ethnic), data=dataset)
  gsr_cont_lm3 = lm(out_var_0 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city +  non_civil + factor(ethnic) + factor(level), data=dataset_0)
  #no lm4 because factor(twocp_cont) =  factor(year)
  gsr_cont_lm5 = lm(out_var_0 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city +  non_civil + factor(ethnic) + factor(level) + factor(region0_eng), data=dataset_0)

  #by headcounts
  gsr_cont_no_lm0 = lm(out_var_1 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city, data=dataset_1)
  gsr_cont_no_lm3 = lm(out_var_1 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city +  non_civil + factor(ethnic) + factor(level), data=dataset_1)
  gsr_cont_no_lm5 = lm(out_var_1 ~  factor(twocp_cont):major_city + factor(twocp_cont) + major_city +  non_civil + factor(ethnic) + factor(level) + factor(region0_eng), data=dataset_1)  
  
  
  
  #cluster standard error by province
  gsr_cont_lm0_se = coef(summary(gsr_cont_lm0,cluster='region1'))[,2]
  gsr_cont_lm3_se = coef(summary(gsr_cont_lm3,cluster='region1'))[,2]
  gsr_cont_lm5_se = coef(summary(gsr_cont_lm5,cluster='region1'))[,2]
  gsr_cont_no_lm0_se = coef(summary(gsr_cont_no_lm0,cluster='region1'))[,2]
  gsr_cont_no_lm3_se = coef(summary(gsr_cont_no_lm3,cluster='region1'))[,2]
  gsr_cont_no_lm5_se = coef(summary(gsr_cont_no_lm5,cluster='region1'))[,2]
  
  
  #regression table setup
  stargazer(gsr_cont_lm0, gsr_cont_lm3, gsr_cont_lm5, gsr_cont_no_lm0, gsr_cont_no_lm3, gsr_cont_no_lm5,
            se=list(gsr_cont_lm0_se,gsr_cont_lm3_se,gsr_cont_lm5_se,
                    gsr_cont_no_lm0_se,gsr_cont_no_lm3_se,gsr_cont_no_lm5_se),
            omit = c('Constant','region0_eng','non_civil','ethnic','level'),
            covariate.labels = c('-2','-1','0','1','2','3','4','majority prefecture',
                                 '-2 year*majority prefecture','-1 year*majority prefecture',
                                 '0 year*majority prefecture','1 year*majority prefecture',
                                 '2 year*majority prefecture','3 year*majority prefecture',
                                 '4 year*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "N", 'Y','N','N','Y'),
                           c("Province Fixed effect",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```


```{r}
#lm_gsr_f = lm_event_did('female', df_wo_police, df_wo_police_tibet)
lm_gsr_m = lm_event_did('male', df_wo_police, df_wo_police_tibet)
```




### triple difference: level of government

```{r}
#define regression function
lm_ddd = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$depar_gsr_f_ratio
    dep_var_1 = dataset_1$depar_gsr_f_no_ratio
  }else{
    dep_var_0 = dataset_0$depar_gsr_m_ratio
    dep_var_1 = dataset_1$depar_gsr_m_no_ratio
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city , data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city  + factor(year) + factor(region0_eng) + factor(level), data=dataset_0)
  gsr_lm6 = lm(formula = dep_var_0 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city  + factor(year) + factor(region0_eng) + pop_total + avg_educ_total + no_elig_ratio + factor(level), data=dataset_0) 
  
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city , data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city  + factor(year) + factor(region0_eng)+ factor(level), data=dataset_1)  
  gsr_no_lm6 = lm(formula = dep_var_1 ~  twocp:major_city + twocp + major_city + base_level + base_level:major_city + base_level:twocp+ base_level:twocp:major_city  + factor(year) + factor(region0_eng) + pop_total + avg_educ_total + no_elig_ratio+ factor(level), data=dataset_1)  
  
  #cluster standard error by province
  gsr_lm0_se = coef(summary(gsr_lm0,cluster='depar_total'))[,2]
  gsr_lm5_se = coef(summary(gsr_lm5,cluster='depar_total'))[,2]
  gsr_lm6_se = coef(summary(gsr_lm6,cluster='depar_total'))[,2]
  gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='depar_total'))[,2]
  gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='depar_total'))[,2]
  gsr_no_lm6_se = coef(summary(gsr_no_lm6,cluster='depar_total'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm5, gsr_lm6, gsr_no_lm0, gsr_no_lm5, gsr_no_lm6,
            se=list(gsr_lm0_se,gsr_lm5_se,gsr_lm6_se,gsr_no_lm0_se,gsr_no_lm5_se,gsr_no_lm6_se),
            omit = c('Constant','region0_eng','year', 'pop_total','avg_educ_total'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```

```{r}
#define regression function
lm_did_minor_ratio = function(gender,dataset_0, dataset_1){
  if(gender == 'female'){
    dep_var_0 = dataset_0$gsr_f
    dep_var_1 = dataset_1$gsr_f_no
  }else{
    dep_var_0 = dataset_0$gsr_m
    dep_var_1 = dataset_1$gsr_m_no
  }
  
  #by jobs
  gsr_lm0 = lm(formula = dep_var_0 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio, data=dataset_0)
  gsr_lm5 = lm(formula = dep_var_0 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio+ non_civil + factor(ethnic) + factor(year) + factor(region0_eng) + factor(level), data=dataset_0)
  gsr_lm6 = lm(formula = dep_var_0 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio+ non_civil + factor(ethnic) + factor(year) + factor(region0_eng) + pop_total + avg_educ_total + no_elig_ratio + factor(level), data=dataset_0) 
  
  
  #by headcounts
  gsr_no_lm0 = lm(formula = dep_var_1 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio, data=dataset_1)
  gsr_no_lm5 = lm(formula = dep_var_1 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio+ non_civil + factor(ethnic) + factor(year) + factor(region0_eng)+ factor(level), data=dataset_1)  
  gsr_no_lm6 = lm(formula = dep_var_1 ~  twocp:pop_minority_ratio + twocp +  pop_minority_ratio+ non_civil + factor(ethnic) + factor(year) + factor(region0_eng) + pop_total + avg_educ_total + no_elig_ratio+ factor(level), data=dataset_1)  
  
  #cluster standard error by province
  gsr_lm0_se = coef(summary(gsr_lm0,cluster='depar_total'))[,2]
  gsr_lm5_se = coef(summary(gsr_lm5,cluster='depar_total'))[,2]
  gsr_lm6_se = coef(summary(gsr_lm6,cluster='depar_total'))[,2]
  gsr_no_lm0_se = coef(summary(gsr_no_lm0,cluster='depar_total'))[,2]
  gsr_no_lm5_se = coef(summary(gsr_no_lm5,cluster='depar_total'))[,2]
  gsr_no_lm6_se = coef(summary(gsr_no_lm6,cluster='depar_total'))[,2]
  
  #regression table setup
  stargazer(gsr_lm0, gsr_lm5, gsr_lm6, gsr_no_lm0, gsr_no_lm5, gsr_no_lm6,
            se=list(gsr_lm0_se,gsr_lm5_se,gsr_lm6_se,gsr_no_lm0_se,gsr_no_lm5_se,gsr_no_lm6_se),
            omit = c('Constant','region0_eng','year', 'pop_total','avg_educ_total'),
            #covariate.labels = c('majority prefecture','UTCP','pseudo civil servant','ethnicity: Han','ethnicity: minority','level: prefecture[1]', 'level: county[2]', 'level: township[3]','UTCP*majority prefecture'),
            omit.stat = c('rsq',"f",'ser'),
            add.lines = list(c("Year Fixed effect", "N", "Y", 'Y','N','Y','Y'),
                           c("Province Fixed effect",  "N", "N", 'Y','N','N','Y')),
            style='aer',
            title= paste("UTCP and Gender Specific Requirement on", gender, sep=" "),
            column.separate = c(3, 3),
            column.labels   = c(paste("whether specifies", gender, sep=" "), paste("headcounts specify", gender, sep=" "),
            align=TRUE))
}
```


```{r}
ddd_gsr_f = lm_ddd('female',agg_depar, agg_depar)
#ddd_gsr_m = lm_ddd('male',agg_depar, agg_depar)

#minor_ratio_gsr_f = lm_did_minor_ratio('female',df_wo_police, df_wo_police_tibet)
#minor_ratio_gsr_m = lm_did_minor_ratio('male',df_wo_police, df_wo_police_tibet)
```








